\textsf{Are large language models superhuman chemists?}

### 2024-03-27 src/tex/appendix.tex
add note about leaderboard

>>>>

\subsection{Leaderboard}
Our leaderboard is based on the toolchain developed for matbench. Briefly, the \chembench pipeline produces standardized files in \texttt{json} format that contributors can add via pull requests to the \chembench repository.
The Markdown tables and plots are then automatically generated and updated on the \chembench website.
